\documentclass{resume} % Use the custom resume.cls style
\usepackage[a4paper, margin=0.4in]{geometry}


%   Heading Section 
\name{Shivank Bali} % Your name
\address{shivankbali.work@gmail.com \\ www.shivankbali.com \\ linkedin.com/in/shivankbali \\ https://github.com/sb565}

\begin{document}

    % Summary

    % \begin{rSection}{Career Objective}
    %  Bachelor of Engineer in Computer Science and Engineering with excellent academic records. Building a career in the field of software and application development. With a keen interest in the subject, I have developed a number of programs in different programming languages and aspire to carry that forward.
    % \end{rSection}


    %	WORK EXPERIENCE SECTION

    \begin{rSection}{Experience}

        \begin{rSubsection}{Software Engineer (Microsoft India)}{Aug 2020 To Present}{}{}

            \item Develop and maintain cloud based services for Microsoft Supply Chain in Deliver space.
            \item Contributed to many REST-API micro-service applications, utilised Azure cloud services.
            \item Moved service from legacy-platform to Kubernetes, reduced latency and improved reliability.
            \item Built tools to automate manual test scenario creation and reduced manual efforts to perform tests.
            
        \end{rSubsection}


        \begin{rSubsection}{Software Engineer Intern (Microsoft India)}{Jan To June 2020 and May To July 2019}{}{}

            \item Developed chat-bot application with tools such as Visual Studio, Azure Cognitive Services and .NET Core.
            \item Used Azure Services to implement Micro-service architectured applications.
            
        \end{rSubsection}


        \begin{rSubsection}{Team Lead / Project Intern (Design and Innovation Centre Lab)}{Jan 2018 To May 2019}{}{}

            \item Worked on research projects with tools and techniques such as image processing, machine learning and neural network-based models for various medical applications and organized workshops on machine learning.

        \end{rSubsection}

    \end{rSection}



    %	EDUCATION SECTION

    \begin{rSection}{Education}

        {\bf UIET Panjab University, Chandigarh} \hfill {\em August 2016 - August 2020} 
        \\ Bachelors in Engineering
        \\ Computer Science and Engineering \hfill{CGPA: 8.76}
        
    \end{rSection}


    %    Projects


    \begin{rSection}{Projects}

        \begin{pSubsection}{Automated detection of Glaucoma using Neural Networks}{Python, Keras, CNN, Machine Learning}{}{}
        
            \item Used Deep-CNN to segment out affected area from Retinal-Fundus images and predict the progression towards glaucoma. Published research paper for this research project in Springer: Multimedia Tools And Applications
            
        \end{pSubsection}
        

        \begin{pSubsection}{Website for Panjab University}{SQL, HTML, CSS, JavaScript, Google Maps API}{}{}
        
            \item Developed front-end web app and location services for Panjab University campus portal, as a summer project for University.
        \end{pSubsection}


        \begin{pSubsection}{Supply Chain Bot (Logistics MS Teams Bot)}{Azure Cognitive Services, Bot Framework}{}{}
        
            \item Created a ChatBot application for Microsoft’s internal use and reduced daily manual effort of sharing data over emails. Chatbot was hosted over Azure and integrated with MS Teams for ease in use.
        \end{pSubsection}
        
        
        \begin{pSubsection}{Line Follower Robot}{Raspberry Pi, OpenCV, Python}{}{}
        
            \item Created a Line-follower robot with provided hardware and software components for E-Yantra competition. Utilised electronic components such as motors, camera and controllers to realize the robot.
        \end{pSubsection}
        
        
        \begin{pSubsection}{Sudoku Solver}{C++, Tesseract-OCR, Python}{}{}
        
            \item Developed a GUI based application to detect sudoku grid from image, recognize digits, digitize the Sudoku and then solve the puzzle and produce the visualized solution.
        \end{pSubsection}

    \end{rSection}

    
    %	TECHNICAL SKILLS

    \begin{rSection}{Technical Skills}

        \begin{tabular}{ @{} >{\bfseries}l @{\hspace{4ex}} l }

            Languages & Python, C++, C, Bash, JS, SQL, C\#. \\
            Artificial Intelligence &  Machine learning, Deep Learning, CNNs, OpenCV. \\
            Cloud(Azure) & Web Apps, Kubernetes, Storage, ServiceBus, CosmosDB, Cognitive Services. \\

        \end{tabular}
        
    \end{rSection}
        

    %	EXAMPLE SECTION
    %----------------------------------------------------------------------------------------

    \begin{rSection}{Achievements}
        \begin{list}{$\cdot$}{\leftmargin=0em}
        
            \itemsep -6pt
                \item Published Research Paper on Automated detection of Glaucoma using deep learning convolution network (G-net) in Springer - Multimedia Tools and Applications.
                \item Certification for Neural Networks and Deep Learning and for Improving Deep Neural Networks: Hyper-parameter tuning, Regularization and Optimization by deeplearning.ai on Coursera.
                \item Qualified for regionals of ICPC 2019 and ICPC 2020.
                \item Winner of Codersbit competition on Interviewbit.com.
                \item Received letter of participation for E-Yantra Robotics Competition.

        \end{list}

    \end{rSection}


\end{document}